Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-28 title.tex
revised abstract

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. These run-time monitors can introduce large overheads in performance
and energy to the system.  Traditionally, these overheads have been an
all-or-nothing cost; monitoring cannot be used if the overheads are considered
too large.  In this paper, we show how a hardware-based dataflow tracking
engine can be used to filter out unnecessary monitoring and to enable partial
monitoring.  We are able to filter out unnecessary monitoring related to clean
metadata in order to greatly reduce the overheads of monitoring. In addition,
we present a hardware architecture can further reduce overheads by enabling a
trade-off between the amount of monitoring performed and the overheads
incurred. In order to prevent false positives due to this partial monitoring,
we extend the dataflow engine to track dropped monitoring flows. We investigate
some of the trade-offs involved with partial monitoring in terms of how closely
an overhead target can be matched versus the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
In our experiments, we see that filtering is able to decrease monitoring
overheads from XX\%-XX\% on average, depending on the monitoring scheme, to
XX\%-XX\%. Additionally, we are able to still achieve XX\% coverage with a 10\%
overhead target.

>>>>

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overhead, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable partial monitoring.
The dataflow engine can identify events with clean metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For the partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from XX\%-XX\% on average, depending on the monitoring scheme, to
XX\%-XX\%. Additionally, the partial monitoring is shown to still achieve XX\% coverage 
only with a 10\% overhead target.
